Wireless service accounting based on Ethereum state channels - Master Thesis

### 2019-10-27 Paper.tex
One more correction

Non-trivial tests covering main work-flows include:
\begin{itemize}
\item Contract requires a minimum value amount to open a channel.
\item A user can open a channel sending value over a minimum amount providing
  in addition an Ethereum ephemeral public key
\item Prevention of channel closing operation using a different private key
  in signature.
\item Ability of the contract owner to close the channel using a properly
  generated user signature.
\item If channel is not closed by the owner, the user, cannot close it
  before a certain amount of time.
\item In case reaching expiration time without the owner properly closing the channel,
  the user can close the channel receiving in return unexpended amount.
\end{itemize}

>>>>

Non-trivial tests covering main work-flows include:
\begin{itemize}
\item Contract requires a minimum value amount to open a channel.
\item A user can open a channel sending value over a minimum amount providing
  in addition an Ethereum ephemeral public key
\item Prevention of channel closing operation using a different private key
  in signature.
\item Ability of the contract owner to close the channel using a properly
  generated user signature.
\item If channel is not closed by the owner, the user, cannot close it
  before a certain amount of time.
\item In case reaching expiration time without the owner properly closing the channel,
  the user can close the channel receiving initial payment amount.
\end{itemize}
